Large Scale Structure Reconstruction with Short-Wavelength Modes

### 2019-10-21 paper/v2.tex

\noindent{\it Conclusion.}\label{sec4}
In this paper, we have proposed a new and potentially powerful method to measure long-wavelength modes without having to actually measure large scale structure directly.
\RC{ State that this is good because we won't be sensitive to observational systematics, sky gradients, dust etc}
\RC{Give a short list of cool things we can do, with references: measure 3D clustering beyond the matter radiation equality turnover for the first time, look for evidence of general relativistic effects which are strongest on large scales (e.g., \cite{Jeong:2012ls}), look for evidence of large scale anomalies, like in the CMB, constrain non-Gaussianity,  etc }\\
Extensions of our work suggest themselves and will be relevant to attempts to apply it to observational data. The noise term $N=A$ would reduce significantly if we go higher into the nonlinear regime while second-order SPT is no longer accurate in this case. Thus, to detect even larger scales, we may need to use contributions from higher order perturbations and expand the integration range to reduce the noise level. \\
Another issue relates to the range of long-wavelength modes that are detectable. In the N-body simulation,  $k_l$ for modes recovered ranged from $2.5 \,h \times 10^{-3}  \rm Mpc^{-1}$ to $1.3\,h\times 10^{-2}  \rm Mpc^{-1}$.If we try to measure smaller modes, the quadratic estimator approach would become inaccurate since the contraction \ec{contraction} is no longer valid in this case.\\ 
Our current formalism for the quadratic estimator for long-wavelength modes is only valid in a box at a fixed time. As the length scales are so large, a more realistic situation should deal with observations on the light cone. The expression for the quadratic estimator to be generalized to take this into account. Moreover, we notice that the upper limit of integration range should also increase if we consider higher redshifts, in order to include more nonlinear information. Finally, when applied to datasets consisting of halos or galaxies, the approach should be modified to include galaxy bias. We also leave this to future work.\\

%\acknowledgements
\onecolumngrid
\Sfigg{real}{Comparison of the true density field in the BigMPDL simulation ($\delta(\vec{x})$ computed using the directly measured large-scale modes, top row) and the density field from the quadratic estimator ($\hat{\delta}(\vec{x})$, middle row). The bottom row shows their difference. Each panel represents a slice through the simulation volume,  $2.5 \,h^{-1}\,\rm Gpc$ wide, and one cell ($0.36 \,h^{-1}\,\rm Gpc$) thick.  The upper limit of $\vk_s$ is $0.22 \,h\, \rm Mpc^{-1}$.}
\twocolumngrid
%\input{main.bbl}

@@

>>>>

\noindent{\it Conclusion.}\label{sec4}
In this paper, we have proposed a new and potentially powerful method to measure long-wavelength modes without having to actually measure large scale structure directly. The estimator works well on an N-Body simulation, so applying this estimator to survey data is an exciting next step. Among the issues that must be faced when dealing with a spectroscopic galaxy survey are: galaxy bias, redshift space distortions, and light-cone effects. We do not expect any of these to be show-stoppers, so it is tempting to speculate about the possibilities that will open up with this estimate of the large scale density field. 
First, we can hope to measure 3D clustering on scales larger than the matter radiation equality turnover without worrying about large-scale systematic effects. General relativistic effects are strongest on large scales (e.g., \cite{Jeong:2012ls}), and these could be detected. There is evidence of large scale anomalies, in the CMB, that could be confronted with maps of large scale structure obtained with this estimator. Primordial non-Gaussianity generated by inflation leaves an imprint on the largest scales. There is even the possibility of cross-correlating the large-scale matter field with the CMB itself to extract information about the longest wavelength modes in the universe. Since the current epoch of acceleration is a large-scale, late-time effect, there is the possibility of learning about the mechanism responsible for acceleration. Although, as mentioned above, challenges remain, there is also the possibility of using even smaller wavelength modes in our estimator by going to higher order in perturbation theory,

%iso ,  etc }\\
%Extensions of our work suggest themselves and will be relevant to attempts to apply it to observational data. The noise term $N=A$ would reduce significantly if we go higher into the nonlinear regime while second-order SPT is no longer accurate in this case. Thus, to detect even larger scales, we may need to use contributions from higher order perturbations and expand the integration range to reduce the noise level. \\
%Another issue relates to the range of long-wavelength modes that are detectable. In the N-body simulation,  $k_l$ for modes recovered ranged from $2.5 \,h \times 10^{-3}  \rm Mpc^{-1}$ to $1.3\,h\times 10^{-2}  \rm Mpc^{-1}$.If we try to measure smaller modes, the quadratic estimator approach would become inaccurate since the contraction \ec{contraction} is no longer valid in this case.\\ 
%Our current formalism for the quadratic estimator for long-wavelength modes is only valid in a box at a fixed time. As the length scales are so large, a more realistic situation should deal with observations on the light cone. The expression for the quadratic estimator to be generalized to take this into account. Moreover, we notice that the upper limit of integration range should also increase if we consider higher redshifts, in order to include more nonlinear information. Finally, when applied to datasets consisting of halos or galaxies, the approach should be modified to include galaxy bias. We also leave this to future work.\\

%\acknowledgements
%\input{main.bbl}

@@

\onecolumngrid
\Sfigg{real}{Comparison of the true density field in the BigMPDL simulation ($\delta(\vec{x})$ computed using the directly measured large-scale modes, top row) and the density field from the quadratic estimator ($\hat{\delta}(\vec{x})$, middle row). The bottom row shows their difference. Each panel represents a slice through the simulation volume,  $2.5 \,h^{-1}\,\rm Gpc$ wide, and one cell ($0.36 \,h^{-1}\,\rm Gpc$) thick.  The upper limit of $\vk_s$ is $0.22 \,h\, \rm Mpc^{-1}$.}
\twocolumngrid
